Assessing primitives performance\\ on multi-stage execution

### 2018-05-17 paper.tex
comment
update plot for linux
update plot for mac

        xtick={1,...,5},

@@

        xticklabels={\legBase, \legSmartSyntaxPlug, \legSlangPlug, \legSlang, \legRTL},

@@

2   0.3411212   0.0006746299
3   0.3375418   0.001577878
4   1.077762   0.005363974
5   2.490423    0.004304882

@@

2   0.6013716   0.0023206431
3   0.5653467   0.007829291
4   1.816869    0.019114984
5   3.537800    0.012357500

@@

2   1.3891212   0.0029489731
3   1.3149840   0.020471694
4   3.818961   0.054523074
5   6.740474    0.010805042

@@

2   8.6795487   0.0586762222
3   8.9585208   0.116958804
4   15.809515   0.300447885
5   16.752667    0.106255682

@@

2   13.6051267   0.0589164968
3   14.7789145   0.147140189
4   24.417751   0.186326223
5   24.480071    0.095038374

@@

    \begin{tikzpicture}
      \begin{axis}
      [
        height=\plotHeight,
        x=0.5cm,
        xtick={1,...,5},
        xticklabel style={rotate=90},
        bar width=0.3cm,
        enlarge x limits={abs=0.45cm},
        xticklabels={\legBase, \legSmartSyntaxPlug, \legSlangPlug, \legSlang, \legRTL},
        font={\footnotesize},
	ybar=10pt,
	ymin=0,
	]
\addplot[
    fill=black!25,
    draw=black,
    point meta=y,
    every node near coord/.style={inner ysep=5pt},
    error bars/.cd,
        y dir=both,
        y explicit
]
table [y error=error] {
x   y           error
1   1           0
2   0.3147064   0.002288488
3   0.3035965   0.001786185
4   0.8545431   0.006132950
5   2.250732    0.04133638
};
      \end{axis}
    \end{tikzpicture}

@@

    \begin{tikzpicture}
      \begin{axis}
      [
        height=\plotHeight,
        x=0.5cm,
        xtick={1,...,5},
        xticklabel style={rotate=90},
        bar width=0.3cm,
        enlarge x limits={abs=0.45cm},
        xticklabels={\legBase, \legSmartSyntaxPlug, \legSlangPlug, \legSlang, \legRTL},
        font={\footnotesize},
	ybar=10pt,
	ymin=0
        ]
\addplot[
    fill=black!25,
    draw=black,
    point meta=y,
    every node near coord/.style={inner ysep=5pt},
    error bars/.cd,
        y dir=both,
        y explicit
]
table [y error=error] {
x   y           error
1   1           0
2   0.5605682   0.002198180
3   0.5566675   0.001023225
4   1.5605275   0.006372279
5   3.754532    0.01109086
};
      \end{axis}
    \end{tikzpicture}

@@

    \begin{tikzpicture}
      \begin{axis}
      [
        height=\plotHeight,
        x=0.5cm,
        xtick={1,...,5},
        xticklabel style={rotate=90},
        bar width=0.3cm,
        enlarge x limits={abs=0.45cm},
        xticklabels={\legBase, \legSmartSyntaxPlug, \legSlangPlug, \legSlang, \legRTL},
        font={\footnotesize},
	ybar=10pt,
	ymin=0
        ]
\addplot[
    fill=black!25,
    draw=black,
    point meta=y,
    every node near coord/.style={inner ysep=5pt},
    error bars/.cd,
        y dir=both,
        y explicit
]
table [y error=error] {
x   y           error
1   1           0
2   1.2505193   0.004611354
3   1.2295801   0.001810171
4   2.8205415   0.008035024
5   7.089806    0.01403785
};
      \end{axis}
    \end{tikzpicture}
    \end{subfigure}
    \begin{subfigure}[b]{.19\textwidth}
 \begin{tikzpicture}
      \begin{axis}
      [
        height=\plotHeight,
        x=0.5cm,
        xtick={1,...,5},
        xticklabel style={rotate=90},
        bar width=0.3cm,
        enlarge x limits={abs=0.45cm},
        xticklabels={\legBase, \legSmartSyntaxPlug, \legSlangPlug, \legSlang, \legRTL},
        font={\footnotesize},
	ybar=10pt,
	ymin=0
        ]
\addplot[
    fill=black!25,
    draw=black,
    point meta=y,
    every node near coord/.style={inner ysep=5pt},
    error bars/.cd,
        y dir=both,
        y explicit
]
table [y error=error] {
x   y           error
1   1           0
2   6.6951738   0.062391122
3   6.6032572   0.024774416
4   10.3029394  0.061481532
5   17.979611   0.10127936
};
      \end{axis}
    \end{tikzpicture}
    \end{subfigure}
    \begin{subfigure}[b]{.19\textwidth}

    \begin{tikzpicture}
      \begin{axis}
      [
        height=\plotHeight,
        x=0.5cm,
        xtick={1,...,5},
        xticklabel style={rotate=90},
        bar width=0.3cm,
        enlarge x limits={abs=0.45cm},
        xticklabels={\legBase, \legSmartSyntaxPlug, \legSlangPlug, \legSlang, \legRTL},
        font={\footnotesize},
	ybar=10pt,
	ymin=0
        ]
\addplot[
    fill=black!25,
    draw=black,
    point meta=y,
    every node near coord/.style={inner ysep=5pt},
    error bars/.cd,
        y dir=both,
        y explicit
]
table [y error=error] {
x   y           error
1   1           0
2   9.4064534   0.036698187
3   9.2138415   0.013982843
4   13.4384830  0.040202717
5   26.404792   0.09298324
};
      \end{axis}
    \end{tikzpicture}

@@

\subsection{Results} %\sk{Results?}

%\cba{Je pense string de taille 0-1 c'est cool pour montrer que le code C va moins vite que pur smalltalk dans ce cas (si c'est vraiment le cas)}
We performed the benchmarks upon five different string sizes: 0, 1, 5, 100 and 1000 characters, using two different compilers: GCC on one hand and LLVM on the other hand. Figure~\ref{fig:bench} shows the results in terms of relative speed-up towards the baseline implementation, respectively for GCC and LLVM.

>>>>

        xtick={1,...,4},

@@

        xticklabels={\legBase, \legSlangPlug, \legSlang, \legRTL},

@@

2   0.4222030   0.0008047936
3   1.028828    0.004597225
4   2.429007    0.002912642

@@

2   0.7673822   0.0011423885
3   1.843189    0.011583771
4   3.517044    0.019675605

@@

2   1.8905825   0.0119153480
3   4.041207   0.061090881
4   7.121638   0.010505603

@@

2   13.1217728   0.0170678541
3   17.708440   0.105891879
4   18.553670   0.023765562

@@

2   25.9913138   0.0320593050
3   24.868577   0.062229078
4   27.454826   0.044223466

@@

    \begin{tikzpicture}
      \begin{axis}
      [
        height=\plotHeight,
        x=0.5cm,
        xtick={1,...,4},
        xticklabel style={rotate=90},
        bar width=0.3cm,
        enlarge x limits={abs=0.45cm},
        xticklabels={\legBase, \legSlangPlug, \legSlang, \legRTL},
        font={\footnotesize},
	ybar=10pt,
	ymin=0,
	]
\addplot[
    fill=black!25,
    draw=black,
    point meta=y,
    every node near coord/.style={inner ysep=5pt},
    error bars/.cd,
        y dir=both,
        y explicit
]
table [y error=error] {
x   y           error
1   1           0
2   0.3841129   0.001065645
3   0.2692461   0.0006797441
4   2.477776   0.009248639
};
      \end{axis}
    \end{tikzpicture}

@@

    \begin{tikzpicture}
      \begin{axis}
      [
        height=\plotHeight,
        x=0.5cm,
        xtick={1,...,4},
        xticklabel style={rotate=90},
        bar width=0.3cm,
        enlarge x limits={abs=0.45cm},
        xticklabels={\legBase, \legSlangPlug, \legSlang, \legRTL},
        font={\footnotesize},
	ybar=10pt,
	ymin=0
        ]
\addplot[
    fill=black!25,
    draw=black,
    point meta=y,
    every node near coord/.style={inner ysep=5pt},
    error bars/.cd,
        y dir=both,
        y explicit
]
table [y error=error] {
x   y           error
1   1           0
2   0.7062775   0.001896893
3   0.4939137   0.0013709049
4   3.744060   0.012604598
};
      \end{axis}
    \end{tikzpicture}

@@

    \begin{tikzpicture}
      \begin{axis}
      [
        height=\plotHeight,
        x=0.5cm,
        xtick={1,...,4},
        xticklabel style={rotate=90},
        bar width=0.3cm,
        enlarge x limits={abs=0.45cm},
        xticklabels={\legBase, \legSlangPlug, \legSlang, \legRTL},
        font={\footnotesize},
	ybar=10pt,
	ymin=0
        ]
\addplot[
    fill=black!25,
    draw=black,
    point meta=y,
    every node near coord/.style={inner ysep=5pt},
    error bars/.cd,
        y dir=both,
        y explicit
]
table [y error=error] {
x   y           error
1   1           0
2   1.7187980   0.005024289
3   1.1879773   0.0033351563
4   7.245105   0.046617323
};
      \end{axis}
    \end{tikzpicture}
    \end{subfigure}
    \begin{subfigure}[b]{.19\textwidth}
 \begin{tikzpicture}
      \begin{axis}
      [
        height=\plotHeight,
        x=0.5cm,
        xtick={1,...,4},
        xticklabel style={rotate=90},
        bar width=0.3cm,
        enlarge x limits={abs=0.45cm},
        xticklabels={\legBase, \legSlangPlug, \legSlang, \legRTL},
        font={\footnotesize},
	ybar=10pt,
	ymin=0
        ]
\addplot[
    fill=black!25,
    draw=black,
    point meta=y,
    every node near coord/.style={inner ysep=5pt},
    error bars/.cd,
        y dir=both,
        y explicit
]
table [y error=error] {
x   y           error
1   1           0
2   12.6151983   0.080605928
3   7.5970353   0.0396763134
4   18.935631  0.124523834
};
      \end{axis}
    \end{tikzpicture}
    \end{subfigure}
    \begin{subfigure}[b]{.19\textwidth}

    \begin{tikzpicture}
      \begin{axis}
      [
        height=\plotHeight,
        x=0.5cm,
        xtick={1,...,4},
        xticklabel style={rotate=90},
        bar width=0.3cm,
        enlarge x limits={abs=0.45cm},
        xticklabels={\legBase, \legSlangPlug, \legSlang, \legRTL},
        font={\footnotesize},
	ybar=10pt,
	ymin=0
        ]
\addplot[
    fill=black!25,
    draw=black,
    point meta=y,
    every node near coord/.style={inner ysep=5pt},
    error bars/.cd,
        y dir=both,
        y explicit
]
table [y error=error] {
x   y           error
1   1           0
2   25.7537381   0.169939301
3   11.6939697   0.0497562584
4   27.829197  0.142897191
};
      \end{axis}
    \end{tikzpicture}

@@

\subsection{Results} 
\cba{Please precise results. x\% for this size showing the problem. y\% for other size so non-existent problem. }

We performed the benchmarks upon five different string sizes: 0, 1, 5, 100 and 1000 characters, using two different compilers: GCC on one hand and LLVM on the other hand. Figure~\ref{fig:bench} shows the results in terms of relative speed-up towards the baseline implementation, respectively for GCC and LLVM.
